The Pagai tool

### 2012-02-15 presentation/pagai.tex
presentation de pagai : tableau de chiffres + slide assert

\usepackage{moy-slides}
\usepackage{tikz}
\usepackage{comment}
\usepackage{listings}

@@

\begin{frame}
	\frametitle{Pagai}
	Compute numerical invariants from an LLVM bitcode file

@@

\begin{frame}
	\frametitle{LLVM IR}
\begin{columns}
	\lstinputlisting{halbwachs-simple.c}
\begin{column}{1cm}
\end{column}
\begin{column}{10cm}
	\includegraphics[width=7cm]{f}
\end{column}
\end{columns}

@@

@@

>>>>

\usepackage{moy-slides}
\usepackage{tikz}
\usepackage{comment}
\usepackage{listings}
\usepackage{array}

@@

\begin{frame}
	\frametitle{Pagai}

	\begin{center}
	Computes numerical invariants from an LLVM bitcode file
	\end{center}

@@

\begin{frame}
	\frametitle{LLVM IR}
\begin{columns}
	\lstinputlisting{halbwachs-simple.c}
\begin{column}{1cm}
\end{column}
\begin{column}{10cm}
	\includegraphics[width=7cm]{f.pdf}
\end{column}
\end{columns}

@@

\begin{frame}[containsverbatim]
	\frametitle{Assert}
Pagai can check that assert are always true.
\begin{columns}
	\lstinputlisting{gopan_assert.c}
\begin{column}{1cm}
\end{column}
\begin{column}{10cm}
\begin{verbatim}
RESULT FOR BASICBLOCK: ------
; <label>:15                                      
  call void @assert_fail(...) 
  unreachable
-----
empty polyhedron of dim (0,0)
ASSERT OK
\end{verbatim}
\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}
	\frametitle{Scalability}

\begin{table}[!h]
	\centering
\begin{tabular}{|l|r|r||r|r|r|r|r|} \hline
	 	 & & &
        \multicolumn{5}{|c|}{Time (in seconds)} 
		\\ \cline{4-8}
		Name & kLOC & $|P_R|$ & S & G & PF & C & DIS \\ \hline
		\input{table_time}
	\hline
\end{tabular}
\label{fig:projects}
\end{table}
